
```{r, setup, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(
  comment = "#>",
  tidy = FALSE,
  error = FALSE,
  fig.width = 8,
  fig.height = 8)
```

# cyclocomp

> Cyclomatic Complecity of R Code

[![Project Status: WIP - Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](http://www.repostatus.org/badges/latest/wip.svg)](http://www.repostatus.org/#wip)
[![Linux Build Status](https://travis-ci.org/MangoTheCat/cyclocomp.svg?branch=master)](https://travis-ci.org/MangoTheCat/cyclocomp)
[![Windows Build status](https://ci.appveyor.com/api/projects/status/github/MangoTheCat/cyclocomp?svg=true)](https://ci.appveyor.com/project/MangoTheCat/cyclocomp)
[![](http://www.r-pkg.org/badges/version/cyclocomp)](http://www.r-pkg.org/pkg/cyclocomp)
[![CRAN RStudio mirror downloads](http://cranlogs.r-pkg.org/badges/cyclocomp)](http://www.r-pkg.org/pkg/cyclocomp)
[![Coverage Status](https://img.shields.io/codecov/c/github/MangoTheCat/cyclocomp/master.svg)](https://codecov.io/github/MangoTheCat/cyclocomp?branch=master)

Cyclomatic complexity is a software metric (measurement), used to indicate
  the complexity of a program. It is a quantitative measure of the number of
  linearly independent paths through a program's source code. It was developed
  by Thomas J. McCabe, Sr. in 1976.

## Installation

```{r eval = FALSE}
devtools::install_github("MangoTheCat/cyclocomp")
```

## Usage

```{r}
library(cyclocomp)
```

`cyclocomp` takes quoted R expressions or function objects,
and returns a single integer, the cyclomatic complexity of the
expression or function.

```{r}
cyclocomp(quote( if (condition) "foo" else "bar" ))
cyclocomp(quote( while (condition) { loop } ))
```

```{r}
cyclocomp(
  function(arg) { calulate(this); and(that) }
)
cyclocomp(ls)
cyclocomp(cyclocomp)
```

Some more examples for the R control structures. A simple `if`
first:

```{r}
cyclocomp(quote({
  if (condition) this
}))
```

An `if` with an `else` branch:

```{r}
cyclocomp(quote({
  if (condition) this else that
}))
  ```

Loops:

```{r}
cyclocomp(quote({
  for (var in seq) expr
}))
```

```{r}
cyclocomp(quote({
  while (cond) expr
}))
```

```{r}
cyclocomp(quote({
  repeat expr
}))
```

`break` and `next` statements add to the complexity:

```{r}
cyclocomp(quote({
  for (var in seq) {
    this
    break
    that
  }
}))
```

```{r}
cyclocomp(quote({
  for (var in seq) {
    this
    next
    that
  }
}))
```

Multiple (explicit or implicit) `return` calls also add to the
complexity:

```{r}
f <- function(arg) {
  if (arg) {
    return("this")
  } else {
    return("that")
  }
  "Otherwise return me"
}
cyclocomp(f)
```


## License

MIT © Mango Solutions
